\begin{abstract}
The selection of a preliminary or final year project can be a complex and daunting task that takes considerable time and structured thinking. Students often struggle with finding suitable project ideas that align with their interests and competencies. Ironically, the abundance of previous project documents available online only adds to the confusion in finding relevant references for their research topics. This creates a need for an organized system that could assist students, working professionals, and developers in generating appropriate project ideas.

IdeaHub is a rule-based recommendation system designed to help users discover relevant projects based on their interests and skill levels. The platform enables users to select from various domains (including Full Stack Development, iOS Development, Machine Learning, and Game Development) and difficulty levels to receive curated project ideas. The system employs a rule-based recommendation engine with an SQLite database for storing and retrieving projects based on user preferences. The backend is developed using Flask and Flask-SQLAlchemy, while the frontend utilizes modern web technologies to provide an intuitive user interface. Projects are sourced from a structured dataset containing GitHub repositories, YouTube tutorials, and research papers, ensuring that users receive practical, educational, and goal-aligned recommendations.

The implementation includes features such as user authentication, personalized project recommendations, and a comprehensive project management system. The system's effectiveness is demonstrated through user testing and feedback, showing significant improvement in project selection efficiency and user satisfaction. Future enhancements include the integration of machine learning algorithms for more personalized recommendations and the expansion of the project database to cover more domains and difficulty levels.
\end{abstract}
